### 2022-09-14 dissertation/chapters/01-introduction.tex
📝 (chapter1): Review fixes

\Ac{ML} is one of the most popular fields of research in \ac{AI} studies today. In recent years, \ac{ML} research has seen some notable achievements in academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \ac{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \ac{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1 \cite{ref:san-hun:2016}.  Furthermore, an improvement on AlphaGo, called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latin word meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1 \cite{ref:silver:2017}.

Over the past few years, modern hardware capabilities have improved to the point where workloads in the field of \ac{ML} that were previously computationally infeasible, are now possible. One such sub-field of \ac{ML} is \acp{ANN}. \acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain \cite{ref:engelbrecht:2007}. \acp{ANN} are the digital equivalent of how we currently understand the brain to work. \acp{ANN} can be trained, which is the equivalent of ``learning'' from data. Learning gives rise to the ability to apply some form of decision making. This ability provides a wide-range of applications from healthcare to finance and yields great interest in the field. With the improvement of hardware came an influx of \ac{ML} researchers that focused their attention on the training of \acp{ANN}.

A popular field of focus for studying \acp{ANN} is the process by which these models are trained. \Acfp{FFNN} are specific types of \acp{ANN} \cite{ref:reed:1999}. The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input and comparing the produced output to that of predefined target data. Training of \acp{ANN} is seen as an optimisation problem. The \ac{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''. A search algorithm known as a \index{heuristic}\textit{heuristic} \cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.

@@

In order to grasp all the concepts that are included in this disseration, it is important to briefly review the landscape of the research fields that are involved, and led to the research work in this disseration. This section provides the reader with a brief summary of the research field and outlines key concepts  that contribute to the topics addressed and discussed in this disseration.

@@

Although the landscape of what can be solved using \acp{ANN} today is extensive, there still exists no single model that can be generalised to solving multiple problem classes, across multiple problem domains. \acs{ANN} training algorithms mostly yield problem specific solutions. This means that a particular approach that works well for one domain of problem class, often does not necessarily work for another. This problem is known as the \ac{NFL} \cite{ref:wolpert:1997}.

@@

A more recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process. This approach focuses on the hybridisation of learning paradigms. The main concept behind this paradigm is that the learning process is dynamic and differs from problem to problem. A particular learning technique might work well for one problem and not for another. At the same time, a particular learning technique might work well for a particular part of the search landscape, but not for another. By dynamically combining the best of different learning paradigms throughout the learning process, a trade-off can be made between exploration and exploitation as is required.

@@

The following section provides the authors motivation for this research and outlines the value that this research brings to the field.

@@

A modern approach is to use \acp{HH} to automate the process of selecting the best heuristic when applied to some optimisation problem. The best heuristic might not be a single heuristic, but rather a hybridisation of heuristics \cite{ref:pillay:2015}. Therefore, careful consideration is required to include and select from a diverse set of heuristics that is capable of solving the given problem. Importantly, only heuristics that are known to have the potential to solve the problem are applicable and can be included in the set of heuristics to select from.

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \ac{HH} by \citeauthor{ref:dowsland:2007} \cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \ac{HH} of \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by \citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} and work done by \citeauthor{ref:vanderstockt:2018} \cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based metaheuristics in real-valued dynamic optimization. However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce. \citeauthor{ref:nel:2021} \cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training. The shortage of research in this field certainly warrants more exploration.

@@

This research takes a particular interest in developing a high-level heuristic that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process. This research develops the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian analysis} which combines prior information with new evidence to the parameters of a selection probability distribution. This selection probability distribution is the mechanism by which the \ac{HH} selects appropriate heuristics to train \acp{FFNN} during the training process (online learning).

@@

      \item Conduct a literature study on \index{meta-learning}meta-learning and \acp{HH} in order to provide the required background information necessary to propose and develop a new high-level heuristic.

@@

The following section outlines the research contributions that this disseration hope to bring to the field.

@@

\begin{itemize}
      \item A novel heuristic selection operator is used that focuses on usi ng Bayesianstatistics to calculate the probability that a heuristic should be selectedin order to efficiently train \acp{FFNN}. The resulting \ac{HH} is referredto as the \Acl{BHH}.

>>>>

\Ac{ML} is one of the most popular fields of research in \ac{AI} studies today. In recent years, \ac{ML} research has seen some notable achievements in academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \ac{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \ac{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1 \cite{ref:san-hun:2016}.  Furthermore, an improvement on AlphaGo, called AlphaZero, learned to play Go  \textit{tabula rasa} \footnote{Latin word meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1 \cite{ref:silver:2017}.

Over the past few years, modern hardware capabilities have improved to the point where workloads in the field of \ac{ML} that were previously computationally infeasible, are now possible. One such sub-field of \ac{ML} is \acp{ANN}. \acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain \cite{ref:engelbrecht:2007}. \acp{ANN} can be trained, which is the equivalent of ``learning'' from data. Learning gives rise to the ability to apply some form of decision making. This ability provides a wide-range of applications from healthcare to finance and yields great interest in the field. With the improvement of hardware came an influx of \ac{ML} researchers that focused their attention on the training of \acp{ANN}.

\Acfp{FFNN} are specific types of \acp{ANN} \cite{ref:reed:1999}. A popular field of focus for studying \acp{ANN} is the process by which these models are trained.  The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input and comparing the produced output to that of predefined target data. Training of \acp{ANN} is seen as an optimisation problem. The \ac{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''. A search algorithm known as a \index{heuristic}\textit{heuristic} \cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.

@@

In order to grasp all the concepts that are included in this disseration, it is important to briefly review the landscape of the research fields that form the basis for the research in this disseration. This section provides the reader with a brief summary of the research field and outlines key concepts that contribute to the topics addressed and discussed in this disseration.

@@

Although the landscape of what can be solved using \acp{ANN} today is extensive, there still exists no single model that can be generalised to solving multiple problem classes, across multiple problem domains. \acs{ANN} training algorithms mostly yield problem specific solutions. This means that a particular approach that works well for one domain or problem class, often does not necessarily work for another. This problem is known as the \ac{NFL} \cite{ref:wolpert:1997}.

@@

A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process. This approach focuses on the hybridisation of learning paradigms. The main concept behind this paradigm is that the learning process is dynamic and differs from problem to problem. A particular learning technique might work well for one problem and not for another. At the same time, a particular learning technique might work well for a particular part of the search landscape, but not for another. By dynamically combining the best of different learning paradigms throughout the learning process, a trade-off can be made between exploration and exploitation as is required.

@@

The following section provides the authors' motivation for this research and outlines the value that this research brings to the field.

@@

In Section \ref{sec:introduction:problem} above, it is mentioned that finding the best heuristic to train \acp{FFNN} is a timely and tedious process. A modern approach is to use \acp{HH} to automate the process of selecting the best heuristic when applied to some optimisation problem. The best heuristic might not be a single heuristic, but rather a hybridisation of heuristics \cite{ref:pillay:2015}. Therefore, careful consideration is required to include and select from a diverse set of heuristics that is capable of solving the given problem. Importantly, only heuristics that are known to have the potential to solve the problem are applicable and can be included in the set of heuristics to select from.

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \ac{HH} by \citeauthor{ref:dowsland:2007} \cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \ac{HH} of \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by \citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} and work done by \citeauthor{ref:vanderstockt:2018} \cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based metaheuristics in real-valued dynamic optimization. However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce. \citeauthor{ref:nel:2021} \cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training. The shortage of research in this field certainly warrants more exploration.

@@

This research takes a particular interest in developing a high-level heuristic that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process. This research develops the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution. This selection probability distribution is the mechanism by which the \ac{HH} selects appropriate heuristics to train \acp{FFNN} during the training process (online learning).

@@

      \item Conduct a literature study on \index{meta-learning}meta-learning and \acp{HH} in order to provide the required background information necessary to propose and develop a new high-level heuristic and selection mechanism.

@@

The following section outlines the research contributions that this disseration yields.

@@

\begin{itemize}
      \item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}. The resulting \ac{HH} is referred to as the \Acl{BHH}.
